Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-25 analysis/paper/paper.Rmd
Update package citations and use inline r code to generate values
This means that when the values in the notes change, the text is updated correspondingly so we have fewer chances of mistakes in reporting values in the results, etc.

Model finesses were evaluated using model summaries and diagnostic plots from 'brms' 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].

Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version 0.10.0) [@Makowski2019].

Data were visualised using 'ggplot2' (version `r packageVersion("ggplot2")`) [@Wickham2016], 'ggpubr' (version `r packageVersion("ggpubr")`) [@Kassambara2020] and patchwork (version `r packageVersion("patchwork")`) [@Pedersen2020].

@@

Forty-eight articles scored 0% out of a possible 100% for reproducibility.
The mean value was 31.2% and the median value was 33.3%.
One article scored 100% or was classed as fully reproducible.
No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.
The majority of the articles were classed as fundamental, 160, with the remaining 138 classed as applied.

Most articles did not make any computational methods available in any fashion with two, 0.007%, classing as '3', which was the highest score available (Figure \@ref(fig:articleScores)A).
Two hundred eighty-seven articles, 96%, were classed as '0' and nine articles, 0.03%, appeared to not use any computational methods.

More articles did a good job of using software that was reasonably available to anyone with 206 scoring '2' or '3' (Figure \@ref(fig:articleScores)B).

>>>>

Model finesses were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].

Probability of direction or maximum probability of effect was plotted, `pd()`, and a test for practical equivalence, `equivalence_test()`, was performed for each model using the contributed R package 'bayestestR' (version `r packageVersion("bayestestR")`) [@Makowski2019].

Data were visualised using 'ggplot2' (version `r packageVersion("ggplot2")`) [@Wickham2016], 'ggpubr' (version `r packageVersion("ggpubr")`) [@Kassambara2020], 'egg' (version `r packageVersion("egg")`) [@Auguie2019] and patchwork (version `r packageVersion("patchwork")`) [@Pedersen2020].

@@

No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.

Out of the `r nrow(rrpp)` articles that were evaluated, `r length(which(rrpp$reproducibility_score == 0))` articles scored 0% out of a possible 100% for reproducibility.
The mean value was `r round(mean(rrpp$reproducibility_score), 1)`% and the median value was `r round(median(rrpp$reproducibility_score), 1)`%.
There were `r length(which(rrpp$reproducibility_score == 100))` (`r round(length(which(rrpp$reproducibility_score == 100))/nrow(rrpp), 2) * 100`%) articles that scored 100% or were classed as fully reproducible.

The majority of the articles, `r length(which(rrpp$art_class == "Fundamental"))`, were classed as fundamental, with the remaining `r length(which(rrpp$art_class != "Fundamental"))` classed as applied.

Most articles did not make any computational methods available in any fashion with `r length(which(rrpp$comp_mthds_avail == 3))` (`r round(length(which(rrpp$comp_mthds_avail == 3))/nrow(rrpp), 3)`%) classified as '3', which was the highest score available (Figure \@ref(fig:articleScores)A).
`r gsub("(^[[:alpha:]])", "\\U\\1", as.character(english(length(which(rrpp$comp_mthds_avail == 0)))), perl = TRUE)` (`r round(length(which(rrpp$comp_mthds_avail == 0))/nrow(rrpp), 2) * 100`%) were classed as '0' and `r as.character(english(length(which(is.na(rrpp$comp_mthds_avail)))))` articles (`r round(length(which(is.na(rrpp$comp_mthds_avail)))/nrow(rrpp), 2) * 100`%) appeared to not use any computational methods.

More articles did a good job of using software that was reasonably available to anyone with `r length(which(rrpp$software_avail >= 2))` (`r round(length(which(rrpp$software_avail >= 2))/nrow(rrpp), 2) * 100`%) scoring '2' or '3' (Figure \@ref(fig:articleScores)B) for software availability.
